Vulnerability Analysis of Container Images in Neuroimaging

### 2020-05-14 paper.tex
discussion added

\begin{comment}
\subsubsection{ReproNim}

ReproNim is a Center for Reproducible Neuroimaging Computation. It is a vision
to help neuroscientists in reproducing neuroimaging research. Repronim
uses RepronIn, BrainVerse, Neuroimaging Computation Environments Manager (NICEMAN),
and NeuroBlast software tools for its
functioning. ReproIn is a software that automate acquisition and conversion
of collected MRI data to BIDS standard format with DataLad version management~\cite{kennedy2019everything}.
BrainVerse is a cross-platform software framework and collaborative desktop application
that helps in managing, tracking, and sharing information.
NICEMAN is a software system that tracks and manages available computation resources
and makes their use in a scalable and reproducible way.
Neuroblast is a service that facilitates data sharing of existing studies, and it also
helps users to search similar studies based on combination of analysis,
tasks and activation patterns. There are currently 28 different Singularity
images used by Repronim.

\subsection{Other images}

\TG{We could also use selected images from DockerHub or SingularityHub. For
instances the ones used by AFNI or other neuroimaging tools not represented
in Boutiques or BIDS Apps. However we wouldn't be able to shrink these
images unless we identified specific command-lines to run.}

\end{comment}

@@

\begin{comment}
Out of the various container image scanning tools available to scan Docker images,
we selected Anchore~\cite{github_2019}
and Vuls~\cite{future-architect_2019} because these are the most mature scanning tools. To scan Singularity images
we use Stools, which is specially designed for Singularity images. This tool internally uses
Clair Scanner tool so we included ClairScanner also in our experiements to compare
performance of both the tools. So total there are three scanners for Docker images
and one scanner for Singularity images.
\end{comment}

@@

If there exist vulnerabilities in the container image, then we can
run after updating the
image. Updating the image involves updating all software packages that are
inside that image. We used a bash script (\href{https://github.com/kaurbhupinder/Vulnerability-Analysis}{Github}) 
to update all images, which checks the
package manager present inside the image and then according to that it
updates the image. However, this option affects the reproducibility
of the image, which means that the image cannot be used to verify the research
findings of other scientists.
\linespread{0.5}
\subsection{Image size Reduction process}

If we want to reduce number of vulnerabilities without effecting the reproducibility of the image,
image size reduction process is a good choice. In this process we reduce the number of packages
installed in the image by deleting unnecessary packages. For that to happen, we need to first figure
out which packages we need for the pipeline to fucntion properly. Here, we used 
Reprozip~\cite{rampin2016reprozip}. It is a tool that
is used to make applications reproducible. It traces operating system calls used by the
application while execution and then based on that it recognizes binaries, files, environment variables,
and library dependencies that will be used by the application for future reexecution. If the OS is
Debian or RPM based, Reprozip also
uses available package manager to acquire a list of distribution packages from where these files come from.
So, we got a list of packages from Reprozip that are needed for the application execution. 
After that, we expanded this list by adding important and required packages that are essential
for the system to function and finally figured out all the dependencies of these packages using Debtree
~\cite{debtree}.
Ultimately, we kept these packages and removed remaining unnecessary packages. We used a bash script
(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/script.sh}{Github}) for getting
a list of unnecessary packages.

@@

Figure~\ref{fig:graph1} gives more image-specific information.
It represents the number of vulnerabilities that are present inside images.
The overall trend of the Figure shows that as the number of packages increases in the image, the number of vulnerabilities
also get increased.
The figure also infers that Alpine distribution, being the
lightweight distribution, have the least number of vulnerabilities, whereas Ubuntu contains highest number of
vulnerabilities. Debian and Centos contain a higher number of critical vulnerabilities than Ubuntu and Alpine.

\begin{table*}
\csvreader[%
 respect all,%
  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
      \begin{adjustbox}{max width=\textwidth},
  after reading=\end{adjustbox},
 tabular={c |c | c | c | c |c},
	table head =Image Labels &{Image names} &{OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
 late after line= \\,
        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
]{results.csv}{}{\csvlinetotablerow}%
       \centering
	\caption{\label{table1}Existing number of Vulnerabilities}
\end{table*}

\begin{comment}
\begin{table}
\csvreader[%
 respect all,%
  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
      \begin{adjustbox}{max width=\columnwidth},
  after reading=\end{adjustbox},
 tabular={c|c},
	table head ={Image Tag} & {Image Name}\\\hline,
 late after line= \\,
        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
]{names.csv}{}{\csvlinetotablerow}%
       \centering
	\caption{\label{table2}Image names}
\end{table}
\end{comment}

\begin{figure}[H]
        {\includegraphics[scale=2.5,width=\columnwidth]
        {Figures/vennDiagram.pdf}}
        \caption{\label{fig:venn} Venn Diagram representing different scanner results}
\end{figure}

\begin{figure*}[!htb]
	{\includegraphics[scale=1.5,width=\textwidth]
	{Figures/vulngraph.pdf}}
        \caption{\label{fig:graph1} Scatterplot representing \#Packages and \#Vulnerabilities}
      \end{figure*}

@@

When the images are rescanned after the update, results changed drastically. However, there are still
vulnerabilities reported by these scanners but there are no fixes available for these vulnerabilities
to date.
\begin{comment}
There are only two
options, either you accept those vulnerabilities and use that image, or you discard that image.
So one thing is clear here that even if we keep our images up to date there will be still some
vulnerabilities that we have to face.
\end{comment}
Figure~\ref{fig:graph2} represents the number of vulnerabilities that are detected by Anchore before and after 
the update of these images.
After the update, the vulnerabilities mostly have \textit{Low, Negligible or Medium} severity status.
Also, after the update, the number of vulnerabilities have a mild slope meaning that there
are a fixed set of packages that contain vulnerabilities and have no fix yet.
\begin{figure*}[!htb]
        {\includegraphics[width=\textwidth]
        {Figures/afterupdatewithpackage.pdf}}
        \caption{\label{fig:graph2} Scatterplot representing the number of vulnerabilities before and 
	after update of the images}
      \end{figure*}
\subsection{Effect Of Size Reduction}

Our last experiment shows deleting unnecessary packages from the image also helps to reduce
the number of vulnerabilities by a significant number. We started this experiment with
\textit{bids/example} image and deleted 61 unnecessary packages out of total 528 packages, which helped
to reduce 838 vulnerabilities to 523. Later, we also checked with \textit{bids/freesurfer} image, which allowed
to delete 71 unnecessary packages out of total 298 packages. Consequently, reducing number of vulnerabilities
from 353 to 101.
\bibliography{bibliography}

>>>>

%\begin{comment}
%\subsubsection{ReproNim}
%
%ReproNim is a Center for Reproducible Neuroimaging Computation. It is a vision
%to help neuroscientists in reproducing neuroimaging research. Repronim
%uses RepronIn, BrainVerse, Neuroimaging Computation Environments Manager (NICEMAN),
%and NeuroBlast software tools for its
%functioning. ReproIn is a software that automate acquisition and conversion
%of collected MRI data to BIDS standard format with DataLad version management~\cite{kennedy2019everything}.
%BrainVerse is a cross-platform software framework and collaborative desktop application
%that helps in managing, tracking, and sharing information.
%NICEMAN is a software system that tracks and manages available computation resources
%and makes their use in a scalable and reproducible way.
%Neuroblast is a service that facilitates data sharing of existing studies, and it also
%helps users to search similar studies based on combination of analysis,
%tasks and activation patterns. There are currently 28 different Singularity
%images used by Repronim. 
%
%\subsection{Other images}
%
%\TG{We could also use selected images from DockerHub or SingularityHub. For
%instances the ones used by AFNI or other neuroimaging tools not represented
%in Boutiques or BIDS Apps. However we wouldn't be able to shrink these
%images unless we identified specific command-lines to run.}
%
%\end{comment}

@@

%\begin{comment}
%Out of the various container image scanning tools available to scan Docker images,
%we selected Anchore~\cite{github_2019}
%and Vuls~\cite{future-architect_2019} because these are the most mature scanning tools. To scan Singularity images
%we use Stools, which is specially designed for Singularity images. This tool internally uses
%Clair Scanner tool so we included ClairScanner also in our experiements to compare
%performance of both the tools. So total there are three scanners for Docker images
%and one scanner for Singularity images.
%\end{comment}

@@

If there exist vulnerabilities in the container image, then we can
run after updating the
image. Updating the image involves updating all software packages that are
inside that image. We used a bash script (\href{https://github.com/kaurbhupinder/Vulnerability-Analysis}{Github}) 
to update all images, which checks the
package manager present inside the image and then according to that it
updates the image. However, this option affects the reproducibility
of the image, which means that the image cannot be used to verify the research
findings of other scientists.
\subsection{Image size Reduction process}
If we want to reduce number of vulnerabilities without effecting the reproducibility of the image,
image size reduction process is a good choice. In this process we reduce the number of packages
installed in the image by deleting unnecessary packages. For that to happen, we need to first figure
out which packages we need for the pipeline to fucntion properly. Here, we used 
Reprozip~\cite{rampin2016reprozip}. It is a tool that
is used to make applications reproducible. It traces operating system calls used by the
application while execution and then based on that it recognizes binaries, files, environment variables,
and library dependencies that will be used by the application for future reexecution. If the OS is
Debian or RPM based, Reprozip also
uses available package manager to acquire a list of distribution packages from where these files come from.
So, we got a list of packages from Reprozip that are needed for the application execution. 
After that, we expanded this list by adding important and required packages that are essential
for the system to function and finally figured out all the dependencies of these packages using Debtree
~\cite{debtree}.
Ultimately, we kept these packages and removed remaining unnecessary packages. We used a bash script
(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/script.sh}{Github}) for getting
a list of unnecessary packages.

@@

Figure~\ref{fig:graph1} gives more image-specific information.
It represents the number of vulnerabilities that are present inside images.
The overall trend of the Figure shows that as the number of packages increases in the image, the number of vulnerabilities
also get increased.
The figure also infers that Alpine distribution, being the
lightweight distribution, have the least number of vulnerabilities, whereas Ubuntu contains highest number of
vulnerabilities. Debian and Centos contain a higher number of critical vulnerabilities than Ubuntu and Alpine.
\begin{table*}
\csvreader[%
 respect all,%
  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
      \begin{adjustbox}{max width=\textwidth},
  after reading=\end{adjustbox},
 tabular={c |c | c | c | c |c},
	table head =Image Labels &{Image names} &{OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
 late after line= \\,
        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
]{results.csv}{}{\csvlinetotablerow}%
       \centering
	\caption{\label{table1}Existing number of Vulnerabilities}
\end{table*}
%\begin{comment}
%\begin{table}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c|c},
%	table head ={Image Tag} & {Image Name}\\\hline,
% late after line= \\,
%        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{names.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{\label{table2}Image names}
%\end{table}
%\end{comment}
\begin{figure}[H]
        {\includegraphics[scale=2.5,width=\columnwidth]
        {Figures/vennDiagram.pdf}}
        \caption{\label{fig:venn} Venn Diagram representing different scanner results}
\end{figure}

\begin{figure*}
	{\includegraphics[scale=1.5,width=\textwidth]
	{Figures/vulngraph.pdf}}
        \caption{\label{fig:graph1} Scatterplot representing \#Packages and \#Vulnerabilities}
      \end{figure*}

@@

When the images are rescanned after the update, results changed drastically. However, there are still
vulnerabilities reported by these scanners but there are no fixes available for these vulnerabilities
to date.
\begin{comment}
There are only two
options, either you accept those vulnerabilities and use that image, or you discard that image.
So one thing is clear here that even if we keep our images up to date there will be still some
vulnerabilities that we have to face.
\end{comment}
Figure~\ref{fig:graph2} represents the number of vulnerabilities that are detected by Anchore before and after 
the update of these images.
After the update, the vulnerabilities mostly have \textit{Low, Negligible or Medium} severity status.
Also, after the update, the number of vulnerabilities have a mild slope meaning that there
are a fixed set of packages that contain vulnerabilities and have no fix yet.
\begin{figure*}
        {\includegraphics[width=\textwidth]
        {Figures/vulnwithupdate.pdf}}
        \caption{\label{fig:graph2} Scatterplot representing the number of vulnerabilities before and 
	after update of the images}
      \end{figure*}
\subsection{Effect Of Size Reduction}

Our last experiment shows deleting unnecessary packages from the image also helps to reduce
the number of vulnerabilities by a significant number. We started this experiment with
\textit{bids/example} image and deleted 61 unnecessary packages out of total 528 packages, which helped
to reduce 838 vulnerabilities to 523. Later, we also checked with \textit{bids/freesurfer} image, which allowed
to delete 71 unnecessary packages out of total 298 packages. Consequently, reducing number of vulnerabilities
from 353 to 101.

\begin{figure*}
        {\includegraphics[scale=1.5,width=\textwidth]
        {Figures/bargraph.png}}
        \caption{\label{fig:bargraph} Bar graph representing \#Vulnerabilities by different experiments}
      \end{figure*}

\subsection{Discussion}

None of the Boutiques and BIDS images at the time of the study are free of vulnerabilities, out of which
some are critical vulnerabilities. Yet there is not a single image scanner on which we can reply upon for
scanning. Additionally, we cannot update all images because some OS already reached end-of-life and are
no longer getting updates. Futhermore, minimization of images is time consuming process. As we have to run
the pipeline to get Reprozip trace that can take upto several hours. Also user should have proper knowledge
of running the pipeline because it is image specific. In addition to that, Reprozip can be only installed
in the images having Python version 2.7.3 or greater, or 3.3 or greater. Also there is no guarantee that
the commands that you ran to get Reprozip trace covered the whole program, may be it run a particular
branch of the program. So there should be some kind of coverage measurement.

\subsection{Conclusion}

In this paper, we performed various experiments to study the security state of the Docker
and Singularity images, which are used in the neuroimaging field. We found out strong correlation
between the number of packages and the number of vulnerabilities in the images, which implies
that the number of vulnerabilities increases with the number of packages. We also found out that
updating images reduces the number of vulnerabilities by a significant number, however they cannot
be made invulnerable.

\bibliography{bibliography}
